\LARGE \bf Energy-Aware Dynamic Planning Algorithm for Autonomous UAVs

### 2020-12-16 icra-2021.tex
I must push this one :S
fixes to the assumption in overview sec

In order to formulate the problem, we considerate some assumptions.

\begin{assm}[Plan periodicity]\label{assm:periodic}
  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$ and current levels of parameters, there exists a constant $n\in\mathbb{Z}_{>0}, n<l$ such that
  \begin{equation*}
    \varphi_i-\varphi_{n+i}=d_i,\,\,\,\forall i\in[l]^+
  \end{equation*}
  where $d_1,\dots,d_l$ are arbitrary constant differences.
\end{assm}

Physically, this means that the plan is periodic.

\begin{defn}[Period]\label{def:period}
  The period $T\in\mathbb{R}_{> 0}$ is defined as the time between $\varphi_i$ and $\varphi_{n+i}$ for an arbitrary $i\in[l]^+$.
\end{defn}

The algorithm measures the time between the stages $\Gamma_i$ and $\Gamma_{n+i}$ and assumes the initial period is one.

@@

\begin{prop}[Rank of the trajectory functions]\label{prop:rank}
  Suppose Assumption~\ref{assm:periodic} holds. Then
  \begin{equation*}
    \mathrm{rank}\begin{bmatrix}
        \varphi_1 & \varphi_{n+1} & \cdots & \varphi_{(l-n)+1} \\ 
        \varphi_2 & \varphi_{n+2} & \cdots & \varphi_{(l-n)+2} \\
        \vdots & \vdots & \ddots & \vdots \\
        \varphi_n & \varphi_{2n} & \cdots & \varphi_l   
      \end{bmatrix}=2.
  \end{equation*}
\end{prop}
\begin{proof} 
  The proof follows directly from Assumption~\ref{assm:periodic}. The column rank of the matrix in the lemma is the dimension of its column space. It denotes the size of the set of all the possible linear combination of the column vectors. We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (the values of the constant differences $d_1,\dots,d_l$ are the same for each $i$). 
\end{proof}

The lemma shows an easy way to verify that a plan is periodic.

\begin{pb}[UAV planning problem]\label{pb}
  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic} and Proposition~\ref{prop:rank}.

  We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ and to derive the path resulting from such plan for the UAV planning problem.
\end{pb}

@@

The control along with the input matrix
\begin{equation}\label{eq:state-control}\begin{split}
  \mathbf{u}&=\begin{bmatrix}c_{i,1} & \cdots & c_{i,\rho} & c_{i,\rho+1} & \cdots & c_{i,\rho+\sigma}\end{bmatrix}^T,\\
  B\mathbf{u}&:=B_i(\mathbf{u}_k-\mathbf{u}_{k-1}),\,\,\,B_i=\left[\begin{array}{c} \nu_i\\\mathbf{0}\end{array}\right],
\end{split}\end{equation}
where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$, $B\in\mathbb{R}^{m\times n}$, and $\mathbf{u}_{-1}=\mathbf{0}$. Moreover, the top row of $B$ contains gain factors $\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho} & \nu_{i,\rho + 1}& \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}$, quantifying the contribution of a given parameter to the instantaneous energy consumption. The other entries of $B$ are zeros.

@@

Let us proof that the plan is periodic and one period is valid, then the plan is valid.

>>>>

In order to formulate the problem, we considerate the assumption.

\begin{assm}[Plan periodicity]\label{assm:periodic}
  Given an initial plan $\Gamma$ consisting of $l$ stages, a generic starting point $\mathbf{p}$ and the current levels of all the parameters $c_{1,1},\dots,c_{l,\rho+\sigma}$, there exists a constant $n\in\mathbb{Z}_{>0}$ ($n<l,l/n\in\mathbb{Z}$) such that
  \begin{equation*}
    \varphi_{(i-1)n+j}\approx \varphi_{in+j},\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
  \end{equation*}
\end{assm}

Physically, this means that the plan is periodic. We will see the assumption being eventually eased for non-periodic plans in Section~\ref{sec:experimental}.

\begin{defn}[Period]\label{def:period}
  The period $T\in\mathbb{R}_{> 0}$ is defined as the time between $\varphi_{(i-1)n+j}$ and $\varphi_{in+j}$ in Assumption~\ref{assm:periodic}.
\end{defn}

The algorithm measures the time between the stages and assumes the initial period is one. We note that periods between stages same stages but different $j$s might be different due to atmospheric interferences.

@@

\begin{prop}[Necessary and sufficient condition for periodicity]\label{prop:rank}
  Suppose Assumption~\ref{assm:periodic} holds, then the plan $\Gamma$ is periodic if
  \begin{equation*}
    \varphi_{(i-1)n+j}-\varphi_{in+j}=d_j,\,\,\,\forall i\in[l/n-1]^+,j\in[n]^+.
  \end{equation*}
  Moreover, if the plan $\Gamma$ is periodic then
  \begin{equation*}
    \mathrm{rank}\begin{bmatrix}
        \varphi_1 & \varphi_{n+1} & \cdots & \varphi_{(l-n)+1} \\ 
        %\varphi_2 & \varphi_{n+2} & \cdots & \varphi_{(l-n)+2} \\
        \vdots & \vdots & \ddots & \vdots \\
        \varphi_n & \varphi_{2n} & \cdots & \varphi_l   
      \end{bmatrix}=2.
  \end{equation*}
\end{prop}
\begin{proof}($\Longleftarrow$) The column rank of the matrix in the lemma is the dimension of its column space. It denotes the size of the set of all the possible linear combination of the column vectors. We note that there is a limited number (two) of linear combinations of the column vectors being these linearly dependent (the difference $d_j$ is the same for any $i$).

  ($\Longrightarrow$) The expression implies that $\varphi_{(i-1)n+j}$ is the same but shifted function in space $\varphi_{(i-1)n+j}=\varphi_{in+j}+d_j$ and $d_j$ is the $j$-th ``shift''. This is equivalent to Assumption~\ref{assm:periodic}.
\end{proof}

The proposition is a necessary ($\Longleftarrow$) and sufficient ($\Longrightarrow$) condition for the periodicity. The algorithm finds $n$ starting from one and finding the value which satisfies the proposition.

\begin{pb}[UAV planning problem]\label{pb}
  Consider an initial plan $\Gamma$ defined in Definition~\ref{def:mission} satisfying Assumption~\ref{assm:periodic}. We are interested in the planning of the path parameters $c_{i,1},\dots,c_{i,\rho}$ and computations parameters $c_{i,\rho+1},\dots,c_{i,\rho+\sigma}$ and to derive the path resulting from such plan for the UAV planning problem.
\end{pb}

@@

The control along with the input matrix
\begin{equation}\label{eq:state-control}\begin{split}
  \mathbf{u}_k&=\begin{bmatrix}c_{k,1} & \cdots & c_{k,\rho} & c_{k,\rho+1} & \cdots & c_{k,\rho+\sigma}\end{bmatrix}^T,\\
  B\mathbf{u}&:=B_i(\mathbf{u}_k-\mathbf{u}_{k-1}),\,\,\,B_i=\left[\begin{array}{c} \nu_i\\\mathbf{0}\end{array}\right],
\end{split}\end{equation}
where $\mathbf{u}\in\mathbb{R}^n$ is the control with $n=\rho+\sigma$, $B\in\mathbb{R}^{m\times n}$, and $\mathbf{u}_{-1}=\mathbf{0}$. Moreover, the top row of $B$ contains gain factors $\nu_i=\begin{bmatrix}\nu_{i,1} & \cdots & \nu_{i,\rho} & \nu_{i,\rho + 1}& \cdots & \nu_{i,\rho+\sigma}\end{bmatrix}$, quantifying the contribution of a given parameter to the instantaneous energy consumption. The other entries of $B$ are zeros.

@@

Let us proof that if the plan is periodic and one period is valid, then the plan is valid.
